## Webscraping test

I've used the rvest library to read the data from the website
https://github.com/hadley/rvest

#### Function with different parameters are written to clean the data from the html data read from the website.

##### Explanation

wp -> A reference to a webpage that is being read, 
selector >- If a CSS class is assigned to a html node then it's very easy to find and read the value. Selector expect you to provide a CSS class info
func -> i've created this function pointer to call any funciton on your data - for example Head, str, names etc 

Cleaning:
By default, i'm removing spaces and newline from the data, however if you have a special requirement for example remove comma etc you can send the info to filter arugment and it will clean it up and repalce it with empty string or any value you would like to provide.

Data converstion:
Sometime it's required to convert the string to number or factor etc. Convert input can help to do that
convert -> as.numeric or as.

```{r}

scrapeData <- function(wp, selector, func = NULL, convert = NULL, filter = NULL, replace = "")
{
  data_html <- rvest::html_nodes(wp,selector)
  
  data <- rvest::html_text(data_html)

  data <- gsub("  ", "", data)
  data <- gsub("\n", "", data)
  
  if(!is.null(filter)){
    data <- gsub(filter, replace, data)
  }
  
  if(!is.null(convert)){
   data <- convert(data)
  }
  
  if (!is.null(func)){
    func(data)
  }
  else{
    data
  }
}

```

```{r}
#install.packages('rvest')
library('rvest')

url <- 'http://www.imdb.com/search/title?count=100&release_date=2016,2016&title_type=feature'

webpage <- read_html(url)

rank_data         <- scrapeData(webpage, ".text-primary", NULL, as.numeric)
title_data        <- scrapeData(webpage, ".lister-item-header a")
description_data  <- scrapeData(webpage,'.ratings-bar+ .text-muted')
runtime_data      <- scrapeData(webpage,'.text-muted .runtime', filter = " min", convert = as.numeric)
genre_data        <- scrapeData(webpage,'.genre', filter = ',.*', convert = as.factor)
rating_data       <- scrapeData(webpage,'.ratings-imdb-rating strong', conver = as.numeric)
votes_data        <- scrapeData(webpage,'.sort-num_votes-visible span:nth-child(2)', filter = ",", as.numeric)
directors_data    <- scrapeData(webpage,'.text-muted+ p a:nth-child(1)', convert = as.factor)
actors_data       <- scrapeData(webpage,'.lister-item-content .ghost+ a', convert = as.factor)
#metascore_data   <- scrapeData(webpage,'.metascore', convert = as.numeric)

```

Above code populated all the data in a variable
Now creating a data.frame obejct from the data populated and then we can generate few graphs

```{r}
movies_df <- data.frame(Rank = rank_data, Title = title_data, Description = description_data, Runtime = runtime_data, Genre = genre_data, Rating = rating_data, 
Votes = votes_data, Director = directors_data, Actor = actors_data)

str(movies_df)

```


### Analyzing scrapped data from the web
```{r}

library('ggplot2')

qplot(data = movies_df,Runtime,fill = Genre,bins = 30)

```

### Question: Based on the above data, which movie from which Genre had the longest runtime?


```{r}
#votes_data
ggplot(movies_df,aes(x=Runtime,y=Rating))+
geom_point(aes(size=Votes,col=Genre))
```
